### 2013-07-19 doc/dissertation/document/chapters/nonlinear_problem/nonlinear_problem.tex
adding backward step output

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lcc}\hline\hline
      \multicolumn{1}{l}{Parameter}& 
      \multicolumn{1}{c}{Value}&
      \multicolumn{1}{c}{Units}\\\hline
      $x_{min}$ & 0.0 & $m$ \\
      $x_{max}$ & 1.0 & $m$ \\
      $y_{min}$ & 0.0 & $m$ \\
      $y_{max}$ & 1.0 & $m$ \\
      $N_x$ & 50 & - \\
      $N_y$ & 50 & - \\
      $DOFs$ & 7803 & - \\
      Density & 1.0 & $kg / m^3$ \\
      Dynamic Viscosity & 0.71 & $(N \times s) / m^2$ \\
      Kinematic Viscosity & 0.71 & $m^2 / s$ \\
      Channel Width & 1.0 & $m$ \\
      Step Height & 0.5 & $m$ \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Backward facing step FANM verification model
      problem parameters.}  \textit{The Navier-Stokes equations in 2
      dimensions are used for the model problem. The Reynolds number
      is varied by modifying the velocity magnitude on the upper
      boundary to induce flow step by inertial forces.}}
  \label{tab:backward_step_parameters}
\end{table}

>>>>

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lcc}\hline\hline
      \multicolumn{1}{l}{Parameter}& 
      \multicolumn{1}{c}{Value}&
      \multicolumn{1}{c}{Units}\\\hline
      $x_{min}$ & 0.0 & $m$ \\
      $x_{max}$ & 25.0 & $m$ \\
      $y_{min}$ & 0.0 & $m$ \\
      $y_{max}$ & 1.0 & $m$ \\
      $N_x$ & 20 & - \\
      $N_y$ & 250 & - \\
      $DOFs$ & 15813 & - \\
      Density & 1.0 & $kg / m^3$ \\
      Dynamic Viscosity & 1.0 & $(N \times s) / m^2$ \\
      Kinematic Viscosity & 1.0 & $m^2 / s$ \\
      Channel Width & 1.0 & $m$ \\
      Step Height & 0.5 & $m$ \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Backward facing step FANM verification model
      problem parameters.}  \textit{The Navier-Stokes equations in 2
      dimensions are used for the model problem. The Reynolds number
      is varied by modifying the velocity magnitude on the upper
      boundary to induce flow step by inertial forces.}}
  \label{tab:backward_step_parameters}
\end{table}
